Multi-Objective Optimization in Image Approximation \\ {} \thanks{The publication has been prepared with the support of Velbazhd Software LLC and Bulgarian Ministry of Education and Science according to the research project No. {D01–205/23.11.2018}.}

### 2020-06-28 Multiobjective-Optimization-in-Image-Approximation/paper.tex
The full text of the paper was written.

All experiments are done with an open-source program written in Java especially for this research \cite{Balabanov-2020}. Apache Commons - Genetic Algorithms \cite{Apache-Commons-Genetic-Algorithms-2020} is used as a Java-based programming library for the optimization part of the program. Apache Commons - Command Line Interface \cite{Apache-Commons-Command-Line-Interface-2020} is used as a Java-based programming library for the program's input parameters handling.

@@

@@

Three separate experiments were executed. As it is shown in Fig. \ref{fig02}-\ref{fig04}, the most informative elements of the bitmap image are kept in the approximated images. There are some deviations in the results, but it is expected because of the probabilistic nature of the genetic algorithms. The count of the ellipses used for the approximation is relatively acceptable, but the presence of obvious blank areas is not of the desired amount.

>>>>

All experiments are done on a single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Oracle Java 1.8.0-91. Experiments are organized as an open-source program written in Java especially for this research \cite{Balabanov-2020}. Apache Commons - Genetic Algorithms \cite{Apache-Commons-Genetic-Algorithms-2020} is used as a Java-based programming library for the optimization part of the program. Apache Commons - Command Line Interface \cite{Apache-Commons-Command-Line-Interface-2020} is used as a Java-based programming library for the program's input parameters handling.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{fig05.png}}
\caption{The result after the fourth run of the experiment.}
\label{fig05}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{fig06.png}}
\caption{The result after the fifth run of the experiment.}
\label{fig06}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{fig07.png}}
\caption{The result after the sixth run of the experiment.}
\label{fig07}
\end{figure}

@@

Six separate experiments were executed. As it is shown in Fig. \ref{fig02}-\ref{fig07}, the most informative elements of the bitmap image are kept in the approximated images. There are some deviations in the results, but it is expected because of the probabilistic nature of the genetic algorithms. The count of the ellipses used for the approximation is relatively acceptable, but the presence of obvious blank areas is not of the desired amount.
